УДК 911.3

### 2024-02-20 legal-companies-migration/Paper.Rmd
Edit styles of document and bibliography, add references in english, other improvements

---
title: "УДК 911.3"
subtitle: "Пространственный анализ миграции юридических компаний в России в 2016–2023 гг. по открытым данным налоговой службы"
author: Сёмин П. О.
output: 
  word_document:
    reference_docx: reference.docx
bibliography: biblio-ru.bib
csl: "biblio-styles-ru.csl"
---

@@

<div custom-style="Title">
Spatial Analysis of Migration of Legal Companies in Russia (2016–2023) Based on Tax Service Open Data
<div>

>>>>

---
title: "УДК 911.3"
subtitle: "Анализ миграции юридических компаний в России в 2016–2023 гг. по открытым данным налоговой службы"
author: Сёмин П. О.
output: 
  word_document:
    reference_docx: reference.docx
bibliography: biblio-ru.bib
csl: "biblio-styles-ru.csl"
---

@@

<div custom-style="Subtitle">
Analysis of Migration of Legal Companies in Russia (2016–2023) Based on Tax Service Open Data
</div>
